Tesseroids: forward modeling gravitational fields in spherical coordinates

### 2015-03-07 manuscript.tex
Acknowledge capes, cnpq and faperj

\todo[inline]{Here's a comment!}

@@

>>>>

\todo[inline]{This is an example of how to leave a comment in a Latex
document.}

@@

The authors were supported in this research by
a fellowship (VCFB) from
Conselho Nacional de Desenvolvimento Cient\'ifico e Tecnol\'ogico (CNPq)
and a scholarship (LU) from
Coordena\c{c}\~ao de Aperfei\c{c}oamento de Pessoal de N\'ivel Superior
(CAPES),
Brazil.
Additional support for the authors was provided by
the Brazilian agencies CNPq (grant 471693/2011-1) and
FAPERJ (grant E-26/103.175/2011).
